---
title: "Display Emergency Hospitalisations"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE)

descriptors = c ("ageYear", "n_risk_gps", "Sex", "age_gp", "covid_vs", "flu_vs", "urban_rural_classification", "simd2020_sc_quintile", "icu_admit_age", "death_28", "hosp_los_gp", "num_prev_admission_gp", "ethnic_gp", "health_board")
descriptors_labels = c ("Age", "Number of Risk Groups", "Sex", "Age Groups", "Covid Vaccination Status",
                        "Flu Vaccination Status", "Urban/Rural Classification", "SIMD", "ICU Admittance", "Death", 
                        "Length of Stay", "Number of previous admissions", "Ethnic Group", "Health Board")

var_labels = setNames(as.list(descriptors_labels), descriptors)
descriptors_death = c("ageYear", "n_risk_gps", "Sex", "age_gp", "covid_vs", "flu_vs", "urban_rural_classification", "simd2020_sc_quintile", "num_prev_admission_gp", "ethnic_gp", "health_board")
descriptors_death_labels = c ("Age", "Number of Risk Groups", "Sex", "Age Groups", "Covid Vaccination Status",
                        "Flu Vaccination Status", "Urban/Rural Classification", "SIMD",  
                        "Number of previous admissions", "Ethnic Group", "Health Board")

var_labels_death = setNames(as.list(descriptors_death_labels), descriptors_death)

```

## Number of Emergency Hospitalisations 
```{r}
num_hosp = nrow(emergency_hosp_cohort)
print(num_hosp)
```


## Hospitalisation - emergency admission description
```{r}
z_df = emergency_hosp_cohort %>% mutate(value = TRUE) %>%
  mutate(MAIN_CONDITION = factor(MAIN_CONDITION)) %>%
  mutate(simd2020_sc_quintile = factor(simd2020_sc_quintile)) %>%
  mutate(icu_admit = as.factor(icu_admit)) %>%
  mutate(health_board = as.factor(health_board)) %>%
  mutate(ethnic_gp = as.factor(ethnic_gp)) %>%
  mutate(death_28 = as.factor(death_28))
z_df = z_df %>% set_variable_labels(.labels=var_labels, .strict=FALSE)

kable(summary_factorlist_wt(z_df, "value", descriptors))
```

## Number of CIST admissions
```{r}
z_df = emergency_hosp_cohort %>% filter(acute_resp_admission == 1 | acute_resp_secondary == 1 |
                                        acute_trauma_admission == 1 | acute_trauma_secondary == 1 |
                                        acute_cancer_admission == 1 | acute_cancer_secondary == 1 |
                                        acute_cardiac_admission == 1 | acute_cardiac_secondary == 1)

print(nrow(z_df))
```

## Hospitalisation - Trauma emergency admission description
```{r}
z_df = emergency_hosp_cohort %>% filter(acute_trauma_admission == 1 | acute_trauma_secondary == 1) %>%
  mutate(value = TRUE) %>%
  mutate(MAIN_CONDITION = factor(MAIN_CONDITION)) %>%
  mutate(simd2020_sc_quintile = factor(simd2020_sc_quintile)) %>%
  mutate(icu_admit = as.factor(icu_admit)) %>%
  mutate(health_board = as.factor(health_board)) %>%
  mutate(ethnic_gp = as.factor(ethnic_gp)) %>%
  mutate(death_28 = as.factor(death_28))
z_df = z_df %>% set_variable_labels(.labels=var_labels, .strict=FALSE)
print(nrow(z_df))
```

```{r}
kable(summary_factorlist_wt(z_df, "value", descriptors))
```

## Hospitalisation - Cardiac emergency admission description
```{r}
z_df = emergency_hosp_cohort %>% filter(acute_cardiac_admission == 1 | acute_cardiac_secondary == 1) %>%
  mutate(value = TRUE) %>%
  mutate(MAIN_CONDITION = factor(MAIN_CONDITION)) %>%
  mutate(simd2020_sc_quintile = factor(simd2020_sc_quintile)) %>%
  mutate(icu_admit = as.factor(icu_admit)) %>%
  mutate(health_board = as.factor(health_board)) %>%
  mutate(ethnic_gp = as.factor(ethnic_gp)) %>%
  mutate(death_28 = as.factor(death_28))
z_df = z_df %>% set_variable_labels(.labels=var_labels, .strict=FALSE)

print(nrow(z_df))
```

```{r}
kable(summary_factorlist_wt(z_df, "value", descriptors))
```

## Hospitalisation - Cancer emergency admission description
```{r}
z_df = emergency_hosp_cohort %>% filter(acute_cancer_admission == 1 | acute_cancer_secondary == 1) %>%
  mutate(value = TRUE) %>%
  mutate(MAIN_CONDITION = factor(MAIN_CONDITION)) %>%
  mutate(simd2020_sc_quintile = factor(simd2020_sc_quintile)) %>%
  mutate(icu_admit = as.factor(icu_admit)) %>%
  mutate(health_board = as.factor(health_board)) %>%
  mutate(ethnic_gp = as.factor(ethnic_gp)) %>%
  mutate(death_28 = as.factor(death_28))
z_df = z_df %>% set_variable_labels(.labels=var_labels, .strict=FALSE)
print(nrow(z_df))
```

```{r}
kable(summary_factorlist_wt(z_df, "value", descriptors))
```

# Hospital Length of stays
```{r}
g = ggplot(emergency_hosp_cohort, aes(hosp_los_gp)) + geom_bar()

print(g)
```

# Weekly counts

## All admissions
```{r}
z_count = emergency_hosp_cohort %>% 
  select(EAVE_LINKNO, ADMISSION_DATE) %>% mutate(t = floor(difftime(ADMISSION_DATE, a_begin, units="weeks"))) %>%
  count(t) %>% mutate(t = t + a_begin) 
g = ggplot() + geom_line(z_count, mapping=aes(x=t, y=n)) + 
  scale_x_date(breaks="1 month", date_labels="%b %Y") + ylab("Number of admissions") +
  xlab("Month and Year") 

print(g)
```

## Produce graphs
```{r}
z_resp = emergency_hosp_cohort %>% filter(acute_resp_admission == 1 | acute_resp_secondary == 1)

z_trauma = emergency_hosp_cohort %>% filter(acute_trauma_admission == 1 | acute_trauma_secondary == 1)

z_cancer = emergency_hosp_cohort %>% filter(acute_cancer_admission == 1 | acute_cancer_secondary == 1)

z_cardiac = emergency_hosp_cohort %>% filter(acute_cardiac_admission == 1 | acute_cardiac_secondary == 1)

z_resp_count = z_resp %>%
  select(EAVE_LINKNO, ADMISSION_DATE) %>% mutate(t = floor(difftime(ADMISSION_DATE, a_begin, units="days"))) %>%
  count(t) %>% mutate(t = t + a_begin) %>% mutate(type="Respiratory")

z_trauma_count = z_trauma %>%
  select(EAVE_LINKNO, ADMISSION_DATE) %>% mutate(t = floor(difftime(ADMISSION_DATE, a_begin, units="days"))) %>%
  count(t) %>% mutate(t = t + a_begin)  %>% mutate(type="Trauma")

z_cancer_count = z_cancer %>%
  select(EAVE_LINKNO, ADMISSION_DATE) %>% mutate(t = floor(difftime(ADMISSION_DATE, a_begin, units="days"))) %>%
  count(t) %>% mutate(t = t + a_begin) %>% mutate(type="Cancer")

z_cardiac_count = z_cardiac %>%
  select(EAVE_LINKNO, ADMISSION_DATE) %>% mutate(t = floor(difftime(ADMISSION_DATE, a_begin, units="days"))) %>%
  count(t) %>% mutate(t = t + a_begin) %>% mutate(type="Cardiac")

z_counts = z_resp_count %>% rbind(z_trauma_count) %>% rbind(z_cancer_count) %>% rbind(z_cardiac_count)
  
g = ggplot(z_counts, aes(x=t)) + geom_line(aes(y=n, color = type)) + 
  scale_x_date(breaks="1 month", date_labels="%b %Y") + ylab("Number of admissions") +
  xlab("Month and Year") 
print(g)
```